---
title: "Exercise_5"
output: html_document
---
# Basic Shiny apps

1.  Create an app that greets the user by name and rank. You may not know all
    the functions you need to do this yet, so some lines are included below.
    Figure out which lines to use and copy them into the ui and server
    components of a Shiny app, perhaps starting with the boilerplate code we
    started with.

    ```{r, eval = FALSE}
    textInput("name", "What's your name?")
    renderText({
      paste0("Hello", input$rank, input$name, collapse = " ")
    })
    renderPlot("histogram", {
      hist(rnorm(1000))
    })
    numericInput("age", "How old are you?")
    textInput("rank", "What's your rank?")
    textOutput("greeting")
    tableOutput("mortgage")

    ```

1.  Suppose your meteorologist friend wants to design an app that lets the user
    set a slider to a temperature in degrees Fahrenheit (`fahr`) between -40 and
    140, and displays the corresponding temperature in Celsius. This is their
    first attempt:

    ```{r, echo = TRUE, out.width = NULL}
    ui <- fluidPage(
      sliderInput("fahr", label = "If the temperature in ° Fahrenheit is",
                  min = -58, max = 122, value = 77),
      "then the temperature in ° Celsius is ",
      textOutput("celsius")
    )

    server <- function(input, output, session) {
      output$celsius <- renderText({
        (fahr - 32) * 5 / 9
      })
    }
    ```

    But unfortunately it has an error:

    ```{r, echo = FALSE, out.width = NULL}
    ## app <- testApp(ui, server)
    ## app_screenshot(app, "basic-app/ex-x-times-5")
    ```

    Can you help them find and correct the error? Your chemist friend wants it
    to also display in Kelvin (freezing is 273.15 K), can you add another output
    for kelvin?

1.  Extend the app from the previous exercise to allow the user to set another
    slider for the relative humidity (between 0 and 100) and display the heat
    index in degrees Fahrenheit and Celsius. The `heat_index_fahr` function is
    included below for computing the heat index from degrees fahrenheit and
    relative humidity. The code for the ui section is already implemented, you
    should only need to replace the lines with comments. Try to reduce
    duplication in the app by using a reactive expression.

    ```{r, echo = TRUE, out.width = NULL}
    ui <- fluidPage(
      sliderInput("fahr", label = "If the temperature in ° Fahrenheit is",
                  min = -58, max = 122, value = 77),
      sliderInput("r", label = "and the relative humidity is",
                  min = 0, max = 100, value = 0),
      "then the heat index in ° Fahrenheit is ",
      textOutput("fahr_hi_out"),
      "and the heat index in ° Celsius is",
      textOutput("celsius_hi")
    )

    server <- function(input, output, session) {
      fahr_hi <- reactive({
        ## maybe define something here to use twice below
      })

      output$fahr_hi_out <- renderText({
        # put some code here
      })

      output$celsius_hi_out <- renderText({
        # put some code here
      })
    }

    heat_index_fahr <- function (t, r) {
      ## https://en.wikipedia.org/wiki/Heat_index#Formula
      cf <- c(
        -8.78469475556, 1.61139411, 2.33854883889, -0.14611605,
        -0.012308094, -0.0164248277778, 0.002211732, 0.00072546,
        -0.000003582)
      cf[1] +
        (cf[2] * t) + (cf[3] * r) +
        (cf[4] * r * t) + (cf[5] * t * t) + (cf[6] * r * r) +
        (cf[7] * t * t * r) + (cf[8] * t * r * r) +
        (cf[9] * t * t * r * r)
    }
    ```

1.  The following app is very similar to one you've seen earlier in the chapter:
    you select a dataset (this time we're using data from the **ggplot2**
    package) and the app prints out a summary and plot of the data. It also
    follows good practice and makes use of reactive expressions to avoid
    redundancy of code. However there are three bugs in the code provided
    below. Can you find and fix them?

    ```{r}
    library(ggplot2)
    datasets <- data(package = "ggplot2")$results[, "Item"]

    ui <- fluidPage(
      selectInput("dataset", "Dataset", choices = datasets),
      verbatimTextOutput("summary"),
      tableOutput("plot")
    )

    server <- function(input, output, session) {
      dataset <- reactive({
        get(input$dataset, "package:ggplot2")
      })
      output$summmry <- renderPrint({
        summary(dataset())
      })
      output$plot <- renderPlot({
        plot(dataset)
      })
    }
    ```
