---
title: "Exercise_3_solution"
output: html_document
---

```{r, include=FALSE}
knitr::opts_chunk$set(fig.width = 12, fig.height = 6)
```
## Setting up the environment

Load ggplot2
```{r}
library(ggplot2)
```

Examine the mtcars dataset
```{r}
head(mtcars)
```

## Scatterplot

### Start with a simple scatterplot


Create a scatterplot from the ```mtcars``` dataset using ```ggplot()```. Set the x variable to ```disp``` and the y variable to ```mpg```.

```{r}
ggplot(mtcars, aes(x =disp, y = mpg)) + geom_point()
```

### Add an aesthetic mapping

Map the color of the points to ```wt```.

```{r}
ggplot(mtcars, aes(x =disp, y = mpg)) + geom_point(aes(color=wt))
```


### Customize the points

Increase the size of the points to a value of 3. Change the color scale to a gradient from low values of ```green``` to high values of ```red```.

```{r}
mtscatter <- ggplot(mtcars, aes(x =disp, y = mpg)) +
                geom_point(aes(color=wt), size=3) +
                scale_color_gradient(low = 'green', high = 'red')

mtscatter
```


### Add another ```geom_``` layer

Use ```geom_smooth()``` and the ```'lm'``` method to add a regression line to the plot.

```{r, message = FALSE, warning=FALSE}
mtscatter + geom_smooth(method = 'lm')
```

## Change the facet labels

Make the facet labels more descriptive using named vectors and the ```facet_grid()``` ```labeller```.

```{r, message = FALSE, warning=FALSE}

# New facet label names for 'am' and 'cyl'
am.labs <- c("Manual", "Automatic")
names(am.labs) <- c(0, 1)

cyl.labs <- c("4 cyl", "6 cyl", "8 cyl")
names(cyl.labs) <- c(4, 6, 8)

# In the facet_grid function, after defining the grid,  use: labeller = labeller(am = am.labs, cyl = cyl.labs)

mtscatter + 
  geom_smooth(method = 'lm') + 
  facet_grid(am ~ cyl, labeller = labeller(am = am.labs, cyl = cyl.labs))
```

### Cleanup the plot

Do the following:

* 'Free' the x axis so that each set of plots by cylinder has its own scale
* Change the theme to black & white with a base size of 14
* Change the following titles:
  + Plot title: "Fuel Economy (1974)" - center
  + X axis title: "Displacement"
  + Y axis title: "MPG"
  + Legend title: "Weight (tons)"

```{r, message = FALSE, warning=FALSE, }
mtscatter +
  geom_smooth(method = 'lm') +
  facet_grid(am ~ cyl, labeller = labeller(am = am.labs, cyl = cyl.labs), scales = "free_x") +
  theme_bw(14) +
  labs(title = "Fuel Economy (1974)", x="Displacement", y = "MPG", color= "Weight (tons)") +
  theme(plot.title = element_text(hjust=0.5))
```


## Final Changes

Now the x axis labels overlap. Fix this by adding 8mm of spacing between panels using ```panel.spacing.x = unit(8, "mm")``` in ```theme```. Plots will resize on rendering to HTML, fixing the crowding on the x axis scale.

```{r, message = FALSE, warning=FALSE}

mtscatter +
  geom_smooth(method = 'lm') +
  facet_grid(am ~ cyl, labeller = labeller(am = am.labs, cyl = cyl.labs), scales = "free_x") +
  theme_bw(14) +
  labs(title = "Fuel Economy (1974)", x="Displacement", y = "MPG", color= "Weight (tons)") +
  theme(plot.title = element_text(hjust=0.5), panel.spacing.x = unit(8, "mm")) 
```

