---
title: "Exercise_2_solution"
output: html_document
---

## Setting up the environment

Load ggplot2, dplyr, and stringr
```{r, message=FALSE}
library(ggplot2)
library(dplyr)
library(stringr)
```

Modify the mpg dataset
```{r}
mpg <- mpg %>% dplyr::mutate(transmission= str_extract(trans, "[:alpha:]*(?=\\()"))
head(mpg)
```

## Boxplot


### Start with a simple boxplot

Create a boxplot from the ```mpg``` dataset using ```ggplot()```. Set the x variable to ```class``` and the y variable to ```hwy```.

```{r}
ggplot(data=mpg, aes(x = class, y = hwy)) + geom_boxplot()
```

### Add an aesthetic mapping

Separate the boxplots for each class by the ```transmission``` type. Hint 1: use the ```color``` aesthetic when changing point colors, and the ```fill``` aesthetic when changing shape colors. Hint 2: adding this maping will separate the boxplots into two different colors, not change the boxplot colors based on some criteria.

```{r}
mpgbox <- ggplot(data=mpg, aes(x = class, y = hwy, fill = transmission)) + geom_boxplot()
mpgbox
```

### Change the plot theme

Set the plot theme to black & white, and increase the base font size to 14.

```{r}
mpgbox + theme_bw(14)
```

### Cleanup titles

Add 'Highway Fuel Economy' as the plot title. Change the x axis title to 'Vehicle Class,' and the y axis title to 'MPG - Highway.'

```{r}
mpgbox + theme_bw(14) +
  labs(title = 'Highway Fuel Economy', x='Vehicle Class', y='MPG - Highway') +
  theme(plot.title = element_text(hjust = 0.5))
```

