---
title: "ggplot2 Quickplot Exercises"
output: html_document
---

## Setting up the environment

Load ggplot2 and other required packages
```{r}
library(ggplot2)
```

Examine the ```mpg``` dataset

```{r, echo=FALSE}
head(mpg)
```

## Default Quickplots

### Quick Histogram

Create a histogram from the ```hwy``` column of the ```mpg``` dataset.

```{r, message=FALSE}
qplot(x=hwy, data=mpg)
```

### Quick Scatterplot

Create a quick scatterplot using the ```mpg``` data. Set the x variable to ```displ``` and the y variable to ```hwy```.

```{r}
qplot(x=displ, y=hwy, data=mpg)
```

## Other Quickplot options

### Quick Boxplot

Create a quick boxplot with the data from ```mpg```. Set the x variable to ```class``` and the y variable to ```hwy```.

```{r}
qplot(x=class, y=hwy, data=mpg, geom="boxplot")
```

### Quick Line Plot

Examine the ```economics``` dataset.

```{r, echo=FALSE}
head(economics)
```

Create a quick line plot from the ```economics``` dataset. Set the x variable to ```date``` and the y variable to ```unemploy```.

```{r}
qplot(x=date, y=unemploy, data=economics, geom="line")
```

Create an area plot using the same data as the line plot above.

```{r}
qplot(x=date, y=unemploy, data=economics, geom="area")
```


