---
title: "ggplot2 Quickplot Exercises"
output: html_document
---

## Setting up the environment

Load ggplot2
```{r}
library(ggplot2)
```

Examine the ```mpg``` dataset

```{r, echo=FALSE}
head(mpg)
```

## Default Quickplots

### Quick Histogram

Create a histogram from the ```hwy``` column of the ```mpg``` dataset.

```{r, warning=FALSE}

qplot(mpg$hwy)

```

### Quick Scatterplot

Create a quick scatterplot using the ```mpg``` data. Set the x variable to ```displ``` and the y variable to ```hwy```.

```{r}

qplot(displ, hwy, data =mpg)

```

## Other Quickplot options

### Quick Boxplot

Create a quick boxplot with the data from ```mpg```. Set the x variable to ```class``` and the y variable to ```hwy```.

```{r}

qplot(class, hwy, data=mpg, geom="boxplot")

```

### Quick Line Plot

Examine the ```economics``` dataset.

```{r, echo=FALSE}
head(economics)
```

Create a quick line plot from the ```economics``` dataset. Set the x variable to ```date``` and the y variable to ```unemploy```.

```{r}



```

Create an area plot using the same data as the line plot above.

```{r}



```


